---
title: "Chapter 6 exercises"
author: "Daryn Cushnie-Sparrow"
date: "July 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###6.1 
6.1. Infrared (IR) spectroscopy technology is used to determine the chemical makeup of a substance. The theory of IR spectroscopy holds that unique molecular structures absorb IR frequencies differently. In practice a spectrometer fires a series of IR frequencies into a sample material, and the device measures the absorbance of the sample at each individual frequency. This series of measurements creates a spectrum profile which can then be used to determine the chemical makeup of the sample material.
A Tecator Infratec Food and Feed Analyzer instrument was used to analyze 215 samples of meat across 100 frequencies. A sample ofthese frequency profiles is displayed in Fig. 6.20. In addition to an IR profile, analytical chemistry determined the percent content of water, fat, and protein for each sample.
If we can establish a predictive relationship between IR spectrum and fat content, then food scientists could predict a sample’s fat content with IR instead of using analytical chemistry. This would provide costs savings, since analytical chemistry is a more expensive, time-consuming process. The matrix `absorp` contains the 100 absorbance values for the 215 samples, while matrix `endpoints` contains the percent of moisture, fat, and protein in columns 1–3, respectively.

(b) In this example the predictors are the measurements at the individual frequencies. Because the frequencies lie in a systematic order (850–1,050nm), the predictors have a high degree of correlation. Hence, the data lie in a
smaller dimension than the total number of predictors (215). Use PCA
to determine the effective dimension of these data. What is the effective dimension?
(c) Split the data into a training and a test set, pre-process the data, and build each variety of models described in this chapter. For those models with tuning parameters, what are the optimal values of the tuning parameter(s)?
(d) Which model has the best predictive ability? Is any model significantly better or worse than the others?
(e) Explain which model you would use for predicting the fat content of a sample.

```{r}
library(caret)
data(tecator)



```

###6.2

Developing a model to predict permeability (see Sect. 1.4) could save significant resources for a pharmaceutical company, while at the same time more rapidly identifying molecules that have a sufficient permeability to become a drug. The matrix fingerprints contains the 1,107 binary molecular predictors for the 165 compounds, while permeability contains permeability response.

(b) The fingerprint predictors indicate the presence or absence of substructures of a molecule and are often sparse meaning that relatively few of the molecules contain each substructure. Filter out the predictors that have low frequencies using the `nearZeroVar` function from the `caret` package. How many predictors are left for modeling?
(c) Split the data into a training and a test set, pre-process the data, and tune a PLS model. How many latent variables are optimal and what is the corresponding resampled estimate of R2?
(d) Predict the response for the test set. What is the test set estimate of R2?
(e) Try building other models discussed in this chapter. Do any have better predictive performance?
(f) Would you recommend any of your models to replace the permeability laboratory experiment?

```{r}
library(AppliedPredictiveModeling)
data(permeability)






```
